---
title: "Introducing openpoweRlifting"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Introducing openpoweRlifting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(openpoweRlifting)

```

openpoweRifting is a library that handles keeping an up-to-date copy of the [OpenPowerlifting](https://www.openpowerlifting.org/) data.

It used to use {pins}, now uses {sqlite} because too big. "Pin" is a nice verb for 
what we're doing, so I'm going to keep it.

# Examples

openpoweRlifting has 2 functions - `pin_opl_ipf` and `pin_opl_full`. 
By default the `pin_opl_ipf` function will grab the [nightly IFP dataset](https://openpowerlifting.gitlab.io/opl-csv/bulk-csv.html) and pin it to 
the table "opl-ipf" in the SQLite database "~/.local/share/opl/opl.db"

You can then read the data with TODO: explain sqlite connections. 

By means of example, I'll find the max totals for each equipment class:

```{r}
#pin_opl_ipf()
location = "~/.local/share/opl/"
con = DBI::dbConnect(RSQLite::SQLite(), file.path(location, "opl-ipf"))

dplyr::tbl(con, "opl") %>% 
  dplyr::group_by(equipment) %>%
  dplyr::slice_max(n=1, order_by=total_kg) %>%
  dplyr::ungroup() %>%
  knitr::kable()
con = DBI::dbDisconnect(con)
```

Similarly, `pin_opl_full()` will grab the full OPL dataset as `"opl-all"`:

```{r}
#pin_opl_all()

con = DBI::dbConnect(RSQLite::SQLite(), file.path(location, "opl-all"))

dplyr::tbl(con, "opl") %>% 
  dplyr::group_by(equipment) %>%
  dplyr::slice_max(n=1, order_by=total_kg) %>%
  dplyr::ungroup() %>%
  knitr::kable()

con = DBI::dbDisconnect(con)
```
